%%%%%%%%%%%%%%%
%							ANALYSIS
%%%%%%%%%%%%%%%

\section{Analysis and Discussion}

%New Paragraph
This section will be the initial discussion of testing, calculations and analysis. Progress made will be discussed here however Section 7 is where the questions are specifically answered. Firstly, this section was used for a draft model to be created for initial testing and current demand expectations. This was to be a temporary estimation until more accurate information was acquired or calculated. The model will break down a custom designed small office floor plan to estimate lighting loads. The creation of this model was from basic square office shapes, hallways and a kitchen. Sizes were estimations based off approximate office sizes from experience viewing offices in Brisbane buildings.  
\newline

%New Paragraph
After the production of the draft model access to QUT schematics, floor layouts and metering data was obtained. Section \ref{section:QUT-Data} will be a breakdown of available data and an analysis of what this means for the remainder of the project. The photovoltaic systems installed also have a secondary metering system that allows for specific monitoring of production curves and comparison to the consumption of the campus. Using this data, production and consumption curves can be estimated and compared so a DC to DC design can be created for feasibility and simulated. This stage will be close to the final model for answering the overall project question of whether this concept is feasible for commercial buildings.    